Logeti, Stockhausen and Koenig:\\Esthetics of Electronic Music

### 2015-07-24 manuscript.tex
Add sketch of Ligeti's ideas in Remifications

>>>>

Ligeti ideals and characteristics as found in Remifications.

\subsubsection{Micropolyphony, flexible rhythm and misleading notation}

This ideas are perhaps the most dominants in this composition.
Examples can be found in the 0:00 - 1:55, 4:20 - 4:35, 5:28 - 6:25.

\subsubsection{Machine like music / Meccanico-type}

It appears to me that these idea could be counted together with the previous ones.
On the other hand, some parts in Remifications are dominated by more ``machine-like'' characteristics than others.
For example: 5:28 - 6:25, 7:00 - 8:00.

\subsubsection{Hectic quality / Gesticulation / Deep-frozen expressionism}

Gesticulated phrases appears in Remifications only for short periods, they are not characterize the composition as a hole.
Nevertheless, we can note two ``overly exaggerated'' phrases, where the primer is a bit more distinct in that manner: 3:36 - 3:45, 6:28 - 6:40.
One could argue that these are just dramatic phrases within the composition, but I suspect that this amount of vibrato in Ligeti's composition most present some decent amount of cynicism.

\subsubsection{‘Mistiness’ to ‘clearing-up’ process}

In my opinion this idea is the lessen distinct in this composition.
This is probably because of the firm voice that accompanies any of the mictrotonal parts, while the ``mistiness'' microtonal is steady and is not ``clearing-up'' into an perfect interval.
The most relevant parts I managed to find for this idea are: 1:40 - 2:08, 2:19 - 2:38.
